---
title: "Index"
author: "AleksandraDurova"
date: "January 17, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
```

## R Markdown
Read in data from 
Alaska Department of Fish and Game, Division of Commercial Fisheries. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1S46Q6M. 

```{r, echo=FALSE}
esc <-read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method="libcurl"),
               header = TRUE,
               stringsAsFactors = F)
#head(esc)#
```

calculate annual, regional total escapement 

*separate dat into year - month- day
* group by and summarize to calculate the sum over unique region-year-species combinations 
*filter for salmon species
```{r, echo=FALSE, warning=FALSE, message=FALSE}
annual_esc <- esc %>%
  separate(sampleDate, into = c("year", "month", "day"), sep= "-") %>% 
  mutate(year = as.numeric(year)) %>%
  group_by(SASAP.Region, Species, year) %>% 
  summarise(escapement = sum(DailyCount)) %>% 
  filter(Species %in% c("Chinook", "Sockeye", "Pink", "Chum", "Coho"))


# %in% filter different species#

```
library (DT) 

```{r, echo=FALSE}
datatable(annual_esc) #dynamic table#
```

#Static Plot

#Interactive Map

we are interested in Species over regions and years

```{r, echo=FALSE}
ggplot(data = annual_esc, mapping = aes(x=Species, y=escapement, fill = SASAP.Region)) + 
  geom_col() #geometry of the plot, coloring always outside of the aes function# fill="name of the variable" colors each the category in diff colors#

```

timeseries for only Kodiak region escapement by species

```{r, echo=FALSE}

my_theme <- theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) #save your formatting for all plots and apply it for all of plots#

ggplot(data = filter(annual_esc, SASAP.Region == "Kodiak"), 
       aes(x=year, y=escapement, color=Species)) +
  geom_line() +
  geom_point() +
  ylab("Escapement") +
  ggtitle("Kodiak Salmon Escapement") +
  my_theme
#you can filter inside in the plot, not creating a new dataframe for each plot#
```

Plot timeseries of escapement by species for all regions 

```{r, echo=FALSE, fig.height=10, fig.width=6}
p<-ggplot(annual_esc, aes(x=year, y=escapement, color=Species)) +
  geom_line() +
  geom_point() +
  facet_wrap(~SASAP.Region, scales = "free", ncol = 2)+ #create many plots at once#
  my_theme

p

ggsave("Figures/region_escapement.png", plot = p, 
       height = 10, 
       width = 8, 
       units = "in")
```

